### 2023-11-07 main.tex
^

	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{c_{1},\ldots,c_{m}=0}^{1}
	f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})

@@

	g_{k}(L,y_{k},c_{k},\ldots,c_{m})=\left(L+2-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}

@@

@@

\textbf{Remark}: In case of $N=2$ we stop distinguishing the types of (non-empty) particles and we retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite[(4.26)]{frassek2020eigenstates}. Indeed, by adapting \eqref{PsiI-N2} we obtain 
 introducing $q=\sum_{j=1}^{m}c_{i}$ in the colour-blind situation \eqref{exactCorrelations} becomes
	\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=&\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{m}=q\}}
	\\&\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}\dt
We observe that, at most $q$ factors do survive in the product over $k$. For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$. For each of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by  
	\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}\dt
We can introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,m\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$ and write 
	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{m}=q\}}\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\left(L+2-y_{\ell_{k}}-(q-k+1)\right)\dt
All in all we have that
\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\frac{\left(L+1-y_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt

>>>>

	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{c_{1},\ldots,c_{m}=0}^{1}
	f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})

@@

	g_{k}(L,x_{k},c_{k},\ldots,c_{m})=\left(L+2-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}

@@

 In case of $N=2$ we stop distinguishing the types of (non-empty) particles and we retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite[(4.26)]{frassek2020eigenstates}:  
	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=1\}}\right]=\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
\textbf{Proof:} Starting from \eqref{exactCorrelations_1} we exploit indistinguishability of particles and we introduce $q=\sum_{k=1}^{m}c_{x_{k}}$, such that $q\in\{0,\ldots,m\}$. There are many values of $c$'s that give the same $q$, therefore we define $q$ labels for the selected particles $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that  $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$. For any $q$, we identify $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ coordinates where the $c_{x_{\ell_{i}}}=1$, then we have that 
		\prod_{k=1}^{m}\left(2+L-x_{k}-\sum_{j=k}^{m}\right)=\prod_{k=1}^{q}\left(1+L-x_{\ell_{k}}-q+k\right)
Moreover, we observe that for fixed $q$ we have
	\frac{\Gamma(2+L-\sum_{k=1}^{m}c_{k})}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}
Varying all possible $c$'s in \eqref{exactCorrelation_1} is equivalent of varying all possible $q$ and all possible $\ell_{1},\ldots,\ell_{q}$, therefore we obtain that 
	\sum_{c_{1}\ldots,c_{m}=0}^{m}\frac{\Gamma(2+L-\sum_{k=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\left(2+L-x_{k}-\sum_{j=k}^{m}\right)=\sum_{q=0}^{m}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{(1+L-x_{\ell_{k}}-q+k)}{(2+L-k)}

@@

\begin{comment}
 introducing $q=\sum_{j=1}^{m}c_{i}$ in the colour-blind situation \eqref{exactCorrelations} becomes
\begin{align}
	\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=&\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{m}=q\}}
	\\&\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}\dt
\end{align}
We observe that, at most $q$ factors do survive in the product over $k$. For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$. For each of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by  
\begin{equation}
	\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}\dt
\end{equation}
We can introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,m\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$ and write 
\begin{equation}
	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{m}=q\}}\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\left(L+2-y_{\ell_{k}}-(q-k+1)\right)\dt
\end{equation}
Moreover, we observe that 
\begin{equation}
	\frac{\Gamma(L+2-q)}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}\dt
\end{equation}
All in all we have that
\end{comment}
